\textbf{NBA Party}

### 2017-07-01 init_model.rnw
Now sorting teams based on distance to NYC for heatmap, re: next day opponent uncorrelated.

load(file = 'tmp_data/covers_lines.RData')
## load(file = 'tmp_data/nmusician_estabs.RData')
load(file = 'tmp_data/population_by_county_year.RData')
load(file = 'tmp_data/nba_musicians.RData')

@@

HOURS <- 24
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) & 
                nhours.lgame <= HOURS & 
                last.game.loc != team]
nba.lines[, party.placebo := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) & 
                nhours.lgame > HOURS & 
                last.game.loc != team]

@@

pdf('writing/next_day_opponent.pdf', width = 14, height = 14)
ggplot(tmp, aes(x = location, y = last.game.loc, fill = log(N))) + 
    geom_tile() +
    facet_wrap(~lst.game + cur.game) + 
    labs(x = 'Current Game Location', y = 'Last Game Location', 
         title = 'Distribution of Next Day Opponent - NBA') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 315, vjust = 0.5),
          plot.title = element_text(hjust=.5))
dev.off()

@@

>>>>

load(file = 'tmp_data/covers_lines.RData')
## load(file = 'tmp_data/nmusician_estabs.RData')
load(file = 'tmp_data/population_by_county_year.RData')
## load(file = 'tmp_data/nba_musicians.RData')
load(file = 'tmp_data/nba_studios.RData')

@@

HOURS <- 24
## nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team & weekdays(date) %in% c('Saturday', 'Sunday'), log(nmusicians+1), 0)]
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) &
                nhours.lgame <= HOURS &
                last.game.loc != team]
nba.lines[, party.placebo := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) &
                nhours.lgame > HOURS &
                last.game.loc != team]

@@

### We sort our table according to last.game.loc distance to NYC to show travel restrictions.
load(file = 'tmp_data/distance_matrix.RData')
dmat <- melt(dmat)
setDT(dmat)
setnames(dmat, c('last.game.loc', 'location', 'distance'))
dmat <- dmat[location == 'brooklyn nets', list(last.game.loc, distance)] 
setorder(dmat, distance)

tmp <- merge(tmp, dmat, by = 'last.game.loc')
setnames(tmp, 'distance', 'distance to NYC')
setorder(tmp, 'distance to NYC')
tmp[, last.game.loc := factor(last.game.loc, levels = dmat[order(distance, decreasing = T), last.game.loc])]
tmp[, location      := factor(location,      levels = dmat[order(distance, decreasing = T), last.game.loc])]

pdf('writing/next_day_opponent.pdf', width = 14, height = 14)
ggplot(tmp, aes(x = location, y = last.game.loc, fill = log(N))) +
    geom_tile() +
    facet_wrap(~lst.game + cur.game) + 
    labs(x = 'Current Game Location', y = 'Last Game Location', 
         title = 'Distribution of Next Day Opponent - NBA\n(sorted by distance to NYC)') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 315, vjust = 0.5),
          plot.title = element_text(hjust=.5))
dev.off()

@@

### We sort our table according to last.game.loc distance to NYC to show travel restrictions.
load(file = 'tmp_data/distance_matrix_mlb.RData')
dmat <- melt(dmat)
setDT(dmat)
setnames(dmat, c('last.game.loc', 'location', 'distance'))
dmat <- dmat[location == 'new york yankees', list(last.game.loc, distance)] 
setorder(dmat, distance)

tmp <- merge(tmp, dmat, by = 'last.game.loc')
setnames(tmp, 'distance', 'distance to NYC')
setorder(tmp, 'distance to NYC')
tmp[, last.game.loc := factor(last.game.loc, levels = dmat[order(distance, decreasing = T), last.game.loc])]
tmp[, location      := factor(location,      levels = dmat[order(distance, decreasing = T), last.game.loc])]
